### 2010-10-14 doc/tech_doc/sec/arc-security-documentation.tex
Enhancing delegation pictures. Fixing figures dependencies in makefile.
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
Spelling correction: It is not transfered but transferred.

%\documentclass{book}
\documentclass{article}                            %for shorter notes
\usepackage{graphicx}                              %for PNG images (pdflatex)
\graphicspath{{./figures/}}
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%\usepackage{trackchanges}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2CM}
\hypersetup{
  pdfauthor = {Weizhong Qiang},
  pdftitle = {Documentation of the ARC security framework},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\begin{figure}
\centering{{{\includegraphics[width=0.9\textwidth]{delegation_flow1.pdf}}}
\caption{\label{fig:delegation_flow1}The flow diagram of delegation procedure with certificate transfered as payload of service specific message} }
\end{figure}

@@

\begin{table}[ht]
\caption{Support of request and protocol in remote policy decision making}
\centering
\begin{tabular}{| l | p{7cm} | p{5cm} |}
\hline
\textbf{  } & \textbf{ARC Request/Response} & \textbf{XACML Request/Response} \\ \hline
\textbf{ARC protocol} & support & support \\ \hline
\textbf{SAML protocol} & not support & support (SAML 2.0 profile of XACML v2.0) \\ \hline
\end{tabular}
\label{table:support_pdp_request_protocol}
\end{table}

>>>>

%\documentclass{book}
\documentclass{article}                            %for shorter notes
\usepackage{graphicx}                              %for PNG images (pdflatex)
\graphicspath{{./figures/}}
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%\usepackage{trackchanges}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2CM}
\hypersetup{
  pdfauthor = {Weizhong Qiang},
  pdftitle = {Documentation of the ARC security framework},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\begin{figure}
\centering{{{\includegraphics[width=0.9\textwidth]{delegation_flow1.pdf}}}
\caption{\label{fig:delegation_flow1}The flow diagram of delegation procedure with certificate transferred as payload of service specific message} }
\end{figure}

@@

\begin{table}[ht]
\caption{Support of request and protocol in remote policy decision making}
\centering
\begin{tabular}{| l | p{7cm} | p{5cm} |}
\hline
\textbf{  } & \textbf{ARC Request/Response} & \textbf{XACML Request/Response} \\ \hline
\textbf{ARC protocol} & supported & supported \\ \hline
\textbf{SAML protocol} & not supported & supported (SAML 2.0 profile of XACML v2.0) \\ \hline
\end{tabular}
\label{table:support_pdp_request_protocol}
\end{table}

### 2010-10-14 doc/tech_doc/xrsl/xrsl-user.tex
Synchronising with ARC0 change - improved description of "notify" attribute
Spelling correction: It is not transfered but transferred.

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string}& file name, local to the
    \textit{Computing Element (CE)}\index{Computing Element}. If this
    string ends with a backslash "/" and \verb#<URL># is empty, the
    entire directory is being kept at the execution site. If however
    this string ends with a backslash "/" but the \verb#<URL>#
    starts with \texttt{gsiftp} or \texttt{ftp}, the whole directory
    is transfered to the destination.\\
    \hspace*{1cm}&\texttt{URL} & URL of the remote file (see
    Section~\ref{sec:url}); if void ("", use the quotes!), the file is
    kept for manual retrieval.  Note that this can not be a local
    \texttt{file://} URL.\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string} & string of the format:
    \verb#[b][q][f][e][c] user1@domain1 [user2@domain2] ...#\\
    \hspace*{1cm}&&here flags indicating the job status are:\\
    \hspace*{1cm}&&\texttt{b} -- begin (PREPARING)\\
    \hspace*{1cm}&&\texttt{q} -- queued (INLRMS)\\
    \hspace*{1cm}&&\texttt{f} -- finalizing (FINISHING)\\
    \hspace*{1cm}&&\texttt{e} -- end (FINISHED)\\
    \hspace*{1cm}&&\texttt{c} -- cancellation (CANCELLED)\\
    \hspace*{1cm}&&\texttt{d} -- deleted (DELETED)\\
  \end{tabular}

>>>>

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string}& file name, local to the
    \textit{Computing Element (CE)}\index{Computing Element}. If this
    string ends with a backslash "/" and \verb#<URL># is empty, the
    entire directory is being kept at the execution site. If however
    this string ends with a backslash "/" but the \verb#<URL>#
    starts with \texttt{gsiftp} or \texttt{ftp}, the whole directory
    is transferred to the destination.\\
    \hspace*{1cm}&\texttt{URL} & URL of the remote file (see
    Section~\ref{sec:url}); if void ("", use the quotes!), the file is
    kept for manual retrieval.  Note that this can not be a local
    \texttt{file://} URL.\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string} & string of the format:
    \verb#[b][q][f][e][c][d] user1@domain1 [user2@domain2] ...#\\
    \hspace*{1cm}&&here flags indicating the job status are:\\
    \hspace*{1cm}&&\texttt{b} -- begin (PREPARING)\\
    \hspace*{1cm}&&\texttt{q} -- queued (INLRMS)\\
    \hspace*{1cm}&&\texttt{f} -- finalizing (FINISHING)\\
    \hspace*{1cm}&&\texttt{e} -- end (FINISHED)\\
    \hspace*{1cm}&&\texttt{c} -- cancellation (CANCELLED)\\
    \hspace*{1cm}&&\texttt{d} -- deleted (DELETED)\\
  \end{tabular}

  When no notification flags are specified, default value of ``\verb#eb#''
  will be used, i.e., notifications will be sent at the job's beginning
  and at its end.

### 2010-10-14 doc/tutorials/ws-programming-tutorial/doc/tex_sec_echoservice/sec_echoservice.tex
Interchange DEBUG and VERBOSE loglevels.
Spelling correction: It is not transfered but transferred.

  \begin{table}[htb]
  \centering
  \caption{List of built-in SecHandlers}
  \label{tbl:list_of_sechandler}
  \begin{tabular*}{\textwidth}[t]{p{4cm}p{11cm}}
	\hline
 	\textbf{identity.map}         & Maps the identity of the user to an identity of the workstation.\\
%					realised by a message attribut.\\
 	\textbf{arc.authz}            & Grants access to the next layer.\\
 	\textbf{delegation.collector} & Processes a request for another service located on a different HED.
                                        A certificate, which has a delegation policy embedded, is transfered to the service running that \textit{SecHandler}. Once the has been extracted and verified it will be transfered
                                        to the requested service.
                                        The policy is now available within the HED of the service such that the client is enabled to access the service.\\
                                        % Question how does the client creates the request - with the SecHandler?
 	\textbf{usernametoken.handler}& Generates the WS-Security username-token and adds it into the SOAP header of outgoing
					 messages. In case of incoming messages the SecHandler extracts the WS-Security username-token out of it. The WS-Security standard extends SOAP and describes i.e. how to attach signatures and encryption header to SOAP messages.\\
	\hline
  \end{tabular*}
  \end{table}
% WS-Security describes how to attach signatures and encryption headers to SOAP messages. In addition, it describes how to attach security tokens, including binary security tokens such as X.509 certificates and Kerberos tickets, to messages.
%
  \begin{table}[htb]
  \centering
  \caption{List of built-in PDPs}
\label{tbl:list_of_pdps}
  \begin{tabular*}{\textwidth}[t]{p{4cm}p{11cm}}
	\hline
 	\textbf{allow.pdp}           & Always returns a positive result.\\
	\textbf{deny.pdp}            & Always returns a negative result.\\
 	\textbf{simplelist.pdp}      & Renders a positive result in case the identity corresponds to the listed ones and additionally 
                                       maps the identity to an user of the workstation.\\
 	\textbf{arc.pdp}             & Evaluates the result based on a policy XML file.\\
 	\textbf{delegate.pdp}        & Similar to \textit{arc.pdp} a policy file will be evaluated. But here, the policy document is 
                                       extracted and transfered
                                       by delegation.collector.\\
 	\textbf{pdpservice.invoker}  & Establishes a connection to special service in order to get a policy decision. The PDP service 
                                       implements the same functionality as ARC PDP, except that the evaluation request and 
                                       response is carried by SOAP messages. The benefit of the PDP Service and the PDP Service
                                       Invoker is that the policy evaluation engine can be accessed remotely and maintained centrally.
\\
	\hline
  \end{tabular*}
  \end{table}
%
%
Due to the fact, that presenting all \textit{SecHandlers} and PDPs would go beyond the scope of an introducing tutorial, only a small set of them will be introduced here in detail. 
Nevertheless, the Tables~\ref{tbl:list_of_sechandler} and~\ref{tbl:list_of_pdps} shall give a first overview about existing \textit{SecHandlers} and \textit{PDPs}. For further reading it is recommended to consult the document ``Security framework of ARC1'' written by Weizhong Qiang and Alexandr Konstantinov. The present chapter is closly related to it.\\

@@

To get an impression in how the requests look like, one can check the log-file (the log level needs to be set to VERBOSE).

>>>>

  \begin{table}[htb]
  \centering
  \caption{List of built-in SecHandlers}
  \label{tbl:list_of_sechandler}
  \begin{tabular*}{\textwidth}[t]{p{4cm}p{11cm}}
	\hline
 	\textbf{identity.map}         & Maps the identity of the user to an identity of the workstation.\\
%					realised by a message attribut.\\
 	\textbf{arc.authz}            & Grants access to the next layer.\\
 	\textbf{delegation.collector} & Processes a request for another service located on a different HED.
                                        A certificate, which has a delegation policy embedded, is transferred to the service running that \textit{SecHandler}. Once the has been extracted and verified it will be transferred
                                        to the requested service.
                                        The policy is now available within the HED of the service such that the client is enabled to access the service.\\
                                        % Question how does the client creates the request - with the SecHandler?
 	\textbf{usernametoken.handler}& Generates the WS-Security username-token and adds it into the SOAP header of outgoing
					 messages. In case of incoming messages the SecHandler extracts the WS-Security username-token out of it. The WS-Security standard extends SOAP and describes i.e. how to attach signatures and encryption header to SOAP messages.\\
	\hline
  \end{tabular*}
  \end{table}
% WS-Security describes how to attach signatures and encryption headers to SOAP messages. In addition, it describes how to attach security tokens, including binary security tokens such as X.509 certificates and Kerberos tickets, to messages.
%
  \begin{table}[htb]
  \centering
  \caption{List of built-in PDPs}
\label{tbl:list_of_pdps}
  \begin{tabular*}{\textwidth}[t]{p{4cm}p{11cm}}
	\hline
 	\textbf{allow.pdp}           & Always returns a positive result.\\
	\textbf{deny.pdp}            & Always returns a negative result.\\
 	\textbf{simplelist.pdp}      & Renders a positive result in case the identity corresponds to the listed ones and additionally 
                                       maps the identity to an user of the workstation.\\
 	\textbf{arc.pdp}             & Evaluates the result based on a policy XML file.\\
 	\textbf{delegate.pdp}        & Similar to \textit{arc.pdp} a policy file will be evaluated. But here, the policy document is 
                                       extracted and transferred
                                       by delegation.collector.\\
 	\textbf{pdpservice.invoker}  & Establishes a connection to special service in order to get a policy decision. The PDP service 
                                       implements the same functionality as ARC PDP, except that the evaluation request and 
                                       response is carried by SOAP messages. The benefit of the PDP Service and the PDP Service
                                       Invoker is that the policy evaluation engine can be accessed remotely and maintained centrally.
\\
	\hline
  \end{tabular*}
  \end{table}
%
%
Due to the fact, that presenting all \textit{SecHandlers} and PDPs would go beyond the scope of an introducing tutorial, only a small set of them will be introduced here in detail. 
Nevertheless, the Tables~\ref{tbl:list_of_sechandler} and~\ref{tbl:list_of_pdps} shall give a first overview about existing \textit{SecHandlers} and \textit{PDPs}. For further reading it is recommended to consult the document ``Security framework of ARC1'' written by Weizhong Qiang and Alexandr Konstantinov. The present chapter is closly related to it.\\

@@

To get an impression in how the requests look like, one can check the log-file (the log level needs to be set to DEBUG).

### 2010-10-14 doc/tutorials/ws-programming-tutorial/doc/tex_tls_echoservice/tls_echoservice.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/
Spelling correction: It is not transfered but transferred.

%\lstsetCPP
%\lstinputlisting
%	[
%	label=lst:tls_echo_service_cpp,
%	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
%	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
%	]
%{../examples/src/services/tlsechoservice/tlsechoservice.cpp}
%
% Lassen wir mal weg....
%
%
% \lstsetKSH
% \begin{lstlisting}[
% label=lst:tls_echo_arched_invoke,float=htb,
% caption={[Transformation in eine uniforme konzentrische Verteilung.]
%          \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
% $ rm -f /var/log/arched.log
% $ arched -c arched_echoservice.xml  && echo jo ||echo n
% $ tail -n100 -f /var/log/arched.log
% $ killall arched
% \end{lstlisting}
% 
%        ...das auch.....

@@

The file containing the client configuration is specified within the command line. 
Its content will be loaded in the code fragment starting at line~\ref{lst_code:tls_echo_client_cpp_getfilecontent}. 
Later, in line~\ref{lst_code:tls_echo_client_cpp_loadconfiguration}, the configuration will be parsed into XML and than transfered into a chain of components which is wrapped by the object \textit{loader}. In order to process a message, an entry point within the chain has to be disclosed. To implement a SOAP client, we are looking for the SOAP component. 
To get the proper component an operator of MCCLoader is used in line~\ref{lst_code:tls_echo_client_cpp_cliententry}.
The previously used class \textit{ClientSOAP} has eased some workload which now has to be done within the client program.
The payloads now have to be wrapped by message objects which have to be initialised with an \textit{MessageAttribute} object and a \textit{MessageContext} object. After the payload has been wrapped within the message it gets transmitted in almost the same way like before, see lines following by line~\ref{lst_code:tls_echo_client_cpp_createandprocess}. The remainder of the source code is identical to the Echo Client.\\

>>>>

%\lstsetCPP
%\lstinputlisting
%	[
%	label=lst:tls_echo_service_cpp,
%	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
%	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
%	]
%{../examples/src/services/tlsechoservice/tlsechoservice.cpp}
%
% Lassen wir mal weg....
%
%
% \lstsetKSH
% \begin{lstlisting}[
% label=lst:tls_echo_arched_invoke,float=htb,
% caption={[Transformation in eine uniforme konzentrische Verteilung.]
%          \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
% $ rm -f /var/log/arc/arched.log
% $ arched -c arched_echoservice.xml  && echo jo ||echo n
% $ tail -n100 -f /var/log/arc/arched.log
% $ killall arched
% \end{lstlisting}
% 
%        ...das auch.....

@@

The file containing the client configuration is specified within the command line. 
Its content will be loaded in the code fragment starting at line~\ref{lst_code:tls_echo_client_cpp_getfilecontent}. 
Later, in line~\ref{lst_code:tls_echo_client_cpp_loadconfiguration}, the configuration will be parsed into XML and than transferred into a chain of components which is wrapped by the object \textit{loader}. In order to process a message, an entry point within the chain has to be disclosed. To implement a SOAP client, we are looking for the SOAP component. 
To get the proper component an operator of MCCLoader is used in line~\ref{lst_code:tls_echo_client_cpp_cliententry}.
The previously used class \textit{ClientSOAP} has eased some workload which now has to be done within the client program.
The payloads now have to be wrapped by message objects which have to be initialised with an \textit{MessageAttribute} object and a \textit{MessageContext} object. After the payload has been wrapped within the message it gets transmitted in almost the same way like before, see lines following by line~\ref{lst_code:tls_echo_client_cpp_createandprocess}. The remainder of the source code is identical to the Echo Client.\\
